Efficient Machine Learning in a Memristor Network

### 2025-01-27 paper/paper.tex
New paper plot with mse and errors

\section{Training Algorithm for a Memristor Network}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights.pdf}
    \caption{}
    \label{fig:cont_disc_gen}
\end{figure}

>>>>

\section{\label{sec:training}Training Algorithm for a Memristor Network}

@@

We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concetration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base to tip radius ratio $R_1 = R_2 = 4$ on each edge. After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibe in \cref{sec:training} that modifies it, while the other parameters are kept constant. 
In \cref{} we show that the cost function decreases of many order
